---
title: "Lab 07 - Modelling course evaluations"
author: [CS Fan Club]
output: 
  tufte::tufte_html:
    css: ../lab.css
    tufte_variant: "envisioned"
    highlight: pygments
link-citations: yes

---

### Load packages 

```{r load-packages, message=FALSE}
library(tidyverse)
library(tidymodels)
library(patchwork)
```

### Read in data

```{r read-data}
evals<-read.csv("data/evals.csv", row.names=1)
```


### Exercise 1

```{r viz-score}
evals %>%
  ggplot() + 
    geom_bar(aes(x = score), color = "blue")

  summary(evals$score)
```

The distribution is left-skewed, this suggests that the majority of students rate the course highly. Summary statistics also demonstrate this claim as the mean score is 4.175 and the median score is 4.3. This is what I expected to see as students were not only taking into account teaching characteristics but also factors such as physical appearance .

### Exercise 2

```{r viz-score-bty}
# add the code for each plot and assign them to the names as outlined below
# remove eval = FALSE from the code chunk options
# knit the document, and you'll see them appear next to each other
# this uses the patchwork package loaded above
# learn more about patchwork at https://patchwork.data-imaginist.com/
# it might be useful for your presentations!
plot_geom_point  <- ggplot(data = evals) + 
  geom_point(aes(x = score, y = bty_avg))

plot_geom_jitter <- ggplot(data = evals) + 
  geom_jitter(aes(x = score, y = bty_avg))

plot_geom_point + plot_geom_jitter
```

Thje geom_jitter functions adds random variation to the points. This helps with over plotting as the original visualization was misleading because certain points were overlapping with others.

### Exercise 3

```{r fit-score_bty_fit}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_bty_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(score~bty_avg, data = evals)
```

```{r tidy-score_bty_fit}
# remove eval = FALSE from the code chunk options after filling in the blanks
tidy(score_bty_fit)
```

score-hat = 3.88 + 0.67 * bty_avg

### Exercise 4

```{r viz-score_bty_fit, eval=FALSE}
plot_geom_jitter <- ggplot(data = evals) + 
  geom_jitter(aes(x = score, y = bty_avg)) + 
  geom_smooth(method = "Im", formula = y~x, se = FALSE, color = "orange")
```

### Exercise 5

*Add interpretation of intercept here.*

### Exercise 6

*Add interpretation of intercept here.*

### Exercise 7

```{r glance-score_bty_fit, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
glance(___)
```

*Add interpretation of R-squared here.*

### Exercise 8

```{r viz-score_bty_fit-diagnostic, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_bty_aug <- augment(score_bty_fit$fit)

ggplot(___)
```

*Add your narrative here.*

### Exercise 9

```{r fit-score_rank_fit}
# fit model

# tidy model output
```

*Add your narrative here.*

### Exercise 10

```{r fit-score_gender_fit}
# fit model

# tidy model output
```

```{r score_gender_intercept, echo = FALSE, eval = FALSE}
# remove eval = FALSE from the code chunk options
score_gender_intercept <- tidy(score_gender_fit) %>% 
  filter(term == "(Intercept)") %>%
  select(estimate) %>%
  pull()
```

```{r score_gender_slope, echo = FALSE, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_gender_slope <- tidy(score_gender_fit) %>% 
  filter(term == "___") %>%
  select(___) %>%
  pull()
```

*Add your narrative here.*

### Exercise 11

```{r fit-score_bty_gender_fit}
# fit model

# tidy model output
```

*Add your narrative here.*

### Exercise 12

```{r glance-score_bty_gender_fit}
# glance model output
```

*Add your narrative here.*

### Exercise 13

*Add your linear model here. Don't worry about math notation, you can use things like score-hat.*

### Exercise 14

*Add your narrative here. One sentence is sufficient.*

### Exercise 15

*Add your narrative here. One sentence is sufficient.*

### Exercise 16

*Add your narrative here. One sentence is sufficient.*

### Exercise 17

*Add your narrative here. One sentence is sufficient.*

### Exercise 18

```{r fit-score_bty_gender_rank_fit}
# fit model

# glance model output
```

*Add your narrative here. One sentence is sufficient.*
